---
title: "week-3-tasks"
author: "Naida Dzigal"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin = 2cm
fontsize: 9pt
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

# Git branch and pull request

Very good mini course \href{https://www.youtube.com/watch?v=RGOj5yH7evk}{here}

# Pull request task

-   fork my repo pull_request_demo
-   clone the forked repository
-   create a rmd file inside HA map with your name, calculate the sum of the -   first 100 integer and create a ggplot.
-   knit into HTML
-   commit and push the 2 files to your forked repo
-   create a pull request to my repo

# Reproduce the followings

```{r, echo = FALSE}
letters1 <- c("a", "b", "c", "d", "e")
print(letters1)
```

```{r, echo = FALSE}
letters2 <- c("a", "c", "e", "g", "i", "k", "m", "o", "q", "s", "u", "w", "y")
print(letters2)
```

```{r, echo = FALSE}
a <- c(1:10)
print(paste0("Count ", a))
```

```{r, echo = FALSE}
print(paste0(letters2, collapse = "#"))
```

```{r, echo = FALSE}
print(paste0(letters2, collapse = " $ "))
```

# Print out the value of

-   pi
-   round pi to two digits
-   square root of pi
-   pi power of 5

```{r, echo = FALSE}
pi
```

```{r, echo = FALSE}
print(signif(pi, digits = 3))
```

```{r, echo = FALSE}
sqrt(pi)
```

```{r, echo = FALSE}
pi^5
```

# Sequences

```{r, echo = FALSE}
seq(0, 1, 0.02)  
```

```{r, echo = FALSE}
seq(1, 2, 1/12)  
```

-   generate a random number between 0 and 1
-   generate 10 random numbers between 0 and 1
-   generate 10 random numbers between 0 and 100
-   generate 20 integer random numbers between 0 and 10 (it should contain 0 and 10 as well and use runif)
-   generate 20 integer random number between 0 and 10 (use sample)

```{r, echo = FALSE}
runif(1)
```


```{r, echo = FALSE}
runif(10, min=0, max=1)
```

```{r, echo = FALSE}
runif(10, min=0, max=100)
```

```{r, echo = FALSE}
runif(20, min=0, max=100)
```

```{r, echo = FALSE}
sample(c(0:10), 20, replace = TRUE)
```

# Vectors

```{r, echo = FALSE}
animals <- c('dog', 'cat', 'mouse', 'uniconr', 'bear', 'snake', 'whale', 'bull' )
```

-   check if ‘bear’ is in the animals vector
-   check if ‘cat’ and ‘snake’ are in the animal vector
-   sum how many of the followings ‘mouse’, ‘wolf’, ‘shark’, ‘bull’ are in the animals vector
-   how many of the animals start with the letter b

```{r, echo = FALSE}
'bear' %in% animals
```

```{r, echo = FALSE}
vals1 <- c('cat', 'snake')
vals1 %in% animals
```

```{r, echo = FALSE}
vals2 <- c('mouse', 'wolf', 'shark', 'bull')
sum(vals2 %in% animals)
```

```{r, echo = FALSE}
sum(startsWith(animals, 'b'))
```

# Lists

```{r}
l <- list('hello', 10, letters)
```

-   print out the second element of the vector
-   print out the length of the vector inside the list
-   check if the number in the list is divisible by 5

```{r, echo = FALSE}
letters[2]
```


```{r, echo = FALSE}
length(letters)
```

```{r, echo = FALSE}
sapply(l[2], `%%`, 5) == 0
```

Plot sinus curve from 0, to 2pi 

```{r, echo = FALSE}
x <- seq(0, 2*pi, length.out = 200)
plot(x, sin(x), type="l", col = "red")
```

# Data type/structures

List as many data type structure as you can!

For example:

```{r}
#numeric
i <- 3
str(i)
```


```{r}
typeof(i)
```

```{r}
# string
s <- 'Hello CEU'
str(s)
```

```{r}
typeof(s)
```


```{r, eval = FALSE}
#
```

# Prettydoc

Install the prettydoc package

```{r, eval = FALSE}
install.packages("prettydoc")
```

Add to the header the following

```{r, eval = FALSE}
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
```


Check the prettydoc themes at [https://prettydoc.statr.me/](https://prettydoc.statr.me/)
